\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Kabeer Vamshee Krishna}} & Email : \href{mailto:kkvamshee@gmail.com}{kkvamshee@gmail.com}\\
  {} & Mobile : +65 91747872 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology Roorkee}{Roorkee, India}
      {Bachelor of Technology in Civil Engineering}{Jul. 2015 -- May. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience and Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Goldman Sachs}{Singapore}
      {Associate}{Jan 2023 - Now}
      \resumeItemListStart
        \resumeItem{}
          {Built JNA Based Java application to establish exchange connectivity with OMnet API.}
        \resumeItem{}
          {Streamlined & automated release process of multi repository systems and integrated with confluence API for documentation. Saving about 3 hours of developer time per month}
        \resumeItem{}
          {Gathered and translated Asia Listed Clearing business requirements into effective software solutions.}
        \resumeItem{}
          {Led resiliency efforts, enhancing stability and served as POC for Listed Clearing Connectivity Apps.}
        \resumeItem{}
          {Cross-functional contributions to Listed Clearing applications beyond standard duties.}
        \resumeItem{}
          {Integrated Prometheus and Grafana with various applications, enabling easy access and real-time monitoring of JVM and EMS metrics. }
        \resumeItem{}
          {Mentored interns and Junior developers, facilitating onboarding and providing insights into both business and technical aspects of applications.}
      \resumeItemListEnd

    \resumeSubheading
      {Goldman Sachs}{Singapore}
      {Analyst}{Nov 2021 - Jan 2023}
      \resumeItemListStart
        \resumeItem{}
          {Implemented solutions to onboard new business for Asia Listed Clearing activity.}
        \resumeItem{}
          {Maintain, enhance, and support External Connectivity Applications for seamless data exchange.}
        \resumeItem{}
          {Designed and implemented a Regression Framework, improving testing efficiency and application reliability.}
        \resumeItem{}
          {Provided dedicated support to a family of External Connectivity applications on a weekly rotation basis, ensuring smooth operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Works Applications}{Singapore}
      {Software Engineer}{Oct 2019 - Oct 2021}
      \resumeItemListStart
        \resumeItem{}
          {Worked on designing and developing an application to simplify \textbf{UI customization} and decrease the communication barrier between clients and consultants.}
        \resumeItem{}
          {Developed and maintained \textbf{Angular Code Generator} to embed flexible design patterns and improve developer productivity saving around \textbf{1200 man hours} and still counting.}
        \resumeItem{}
          {Utilise \textbf{App Dynamics} to analyse and improve \textbf{latency issues} in web applications.}
        \resumeItem{}
          {Actively worked on converting \textbf{JSON data to XLSX/Google Sheets} with embedded macros to enhance ease of usage.}
        \resumeItem{}
          {Handling deployement in internal applications corresponding to \textbf{AWS Lambda} and traditional servers.}
        \resumeItem{}
          {Interacted regularly with managers, consultants to effectively map business requirements to technical requirements in a multicultural workspace.}
      \resumeItemListEnd

    \resumeSubheading
      {Spookfish Innovations}{Bangalore, India}
      {Deep Learning Engineer (Internship)}{May 2018 - Jul 2018}
      \resumeItemListStart
        \resumeItem{}
          {Research and Development of a Human Pose Estimation Architecture.}
        \resumeItem{}
          {Integration of Pose Estimation model with Thermal imagery.}
        \resumeItem{}
          {Calibration of thermal camera with regular RGB camera.}
        \resumeItem{}
          {Development of Pose Comparison model.}
        \resumeItem{}
          {This software is now being used by cricket players in identifying the critical body parts while playing.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Indian Institute of Technology}{Roorkee, India}
      {Research}{Aug 2018 - May 2019}
      \resumeItemListStart
        \resumeItem{}
          {Development of a self-driving motor robot for indoor environments.}
        \resumeItem{}
          {Kinect is used to obtain the depth image instead of LIDAR thereby reducing the cost of model by 50\%.}
        \resumeItem{}
          {Several 3D-mazes are built using Blender for optimization of mapping algorithm.}
        \resumeItem{}
          {Exploration algorithm is being developed to build the map of an unknown space.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages : }{Java, Javascript, Typescript, Bash, Python, C/C++, SQL, HTML, CSS}
    }
    \item{
      \textbf{Frameworks \& Technologies : }{Spring, Angular, React, Node.js, Git, MySQL, DB2, Sybase, Kafka, Docker, Prometheus, Grafana}
    }
    \item{
      \textbf{Interests : }{Web Development, Data Analysis/Visualisation, Machine Learning, Computer Vision}
    }
  \resumeSubHeadingListEnd
  
\section{Awards}
  \resumeSubHeadingListStart
    \item{
      {Secured 3rd Rank in The Young Optimization Crackerjack Contest conducted by IEOR @ IITB \& McKinsey Knowledge Centre India.}
    }
    \item{
      {Ranked 4th in GSC-Brainwaves Hackathon by Societe Generale.}
    }
  \resumeSubHeadingListEnd

\section{Languages}
  \resumeSubHeadingListStart
    \item{
      {English, Hindi, Telugu.}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}